Improved Quasi-Static Methods in Rattlesnake

### 2016-06-12 doc/NEAMS_Report/NEAMS_Report.tex
NEAMS Report: Lots of changes, only a conclusion is needed

\usepackage{vmargin}
\usepackage{color}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amstext}
\usepackage{amsbsy}
%\usepackage{mathbbol}
\usepackage{graphicx} 
\usepackage{verbatim}
\usepackage{csvsimple} 
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{tikz}

@@

@@

\title{Improved Quasi-Static Methods in RATTLESNAKE}
\subtitle{Development and Implementation of Improved Quasi-Static (IQS) methods for time-dependent neutron diffusion and neutron transport solvers in RATTLESNAKE}
\author{ \normalsize
  \textbf{Zachary M. Prince$^\dagger$, Jean C. Ragusa$^\dagger$, Yaqi Wang$^\star$} \\
 \normalsize $^\dagger$Department of Nuclear Engineering \\
 \normalsize Texas A\&M University, College Station, TX, USA\\
 \normalsize $^\star$Idaho National Laboratory\\
 \normalsize \href{mailto:zachmprince@tamu.edu}{zachmprince@tamu.edu}, \href{jean.ragusa@tamu.edu}{jean.ragusa@tamu.edu}, \href{yaqi.wang@inl.gov}{yaqi.wang@inl.gov} 
}

@@

\tcb{I will fix the cover page and page footers later}

\tcb{I removed CFEM from the title}

\tcr{you need Yaqi's concurrence since you list him as co-author}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tcr{we need a short abstract}

@@

\begin{figure}[!htpb]
\centering
\begin{tikzpicture}[
redbox/.style = {rectangle, rounded corners, draw, align=center, top color=white, bottom color=red!20, ultra thick, minimum size=20mm}, 
bluebox/.style = {rectangle, rounded corners, draw, align=center, top color=white, bottom color=blue!20, ultra thick, minimum size=20mm},
greenbox/.style = {rectangle, rounded corners, draw, align=center, top color=white, bottom color=green!20, ultra thick, minimum size=20mm},
every node/.style       = {font=\large}
]
\node[redbox](iqs) at (0,0) {IQS};
\node[bluebox](shape) at (6,2) {Shape};
\node[greenbox](prke) at (11,2) {PRKE};
\node[bluebox](mp) at (6,-2) {Multi-Physics};

\draw[<->,ultra thick,](iqs.north east) -- node[above,sloped] {Picard}(shape.west);
%\draw[<->,ultra thick](iqs.east) -- node[above] {Picard}(prke.west);
\draw[<->,ultra thick](iqs.south east) -- node[below,sloped] {Picard} (mp.west);

\draw[->,ultra thick](prke.south) to [bend left=60] node[above,sloped,midway] {$p,\frac{dp}{dt}$}(shape.south);
\draw[->,ultra thick](shape.east) -- (prke.west) node[above,sloped,midway] {$\rho,\bar{\beta},\bar{\lambda},\Lambda$};

@@

The IQS executioner derives from the Transient executioner in MOOSE.  The IQS executioner contains a loop over micro time steps that computes the PRKE and then passes $p$ and $\frac{dp}{dt}$ for the Transient executioner to evaluate the shape equation at each macro step.  The PRKE is computed with a user specified option of backward-Euler, Crank-Nicolson, or SDIRK33.   The IQS executioner also supplements Transient Picard iteration process by adding its own error criteria:
\be
Error_{IQS}=\left|\frac{\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^{g,n}\right)}{\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^{g,0}\right)}-1\right|
\ee

@@

The input deck for IQS is very similar to the current transient diffusion input file.  The IQS input has a different executioner type and parameters.  The executioner type is simply IQS and input parameters include number of micro time steps, IQS error tolerance, and initial power.  The Rattlesnake transient action system currently requires a multi-app and transfer to compute and pass the initial $\phi$ and $\keff$, which is present in the transient input deck.  However, IQS also requires an initial evaluation of the adjoint flux, for the weighting function.  So another input file and multi-app transfer was made for the adjoint calculation.  An example input file with detailed commentary can be found in the Appendix.

\tcr{in the yak manual you may find how to incorporate nicely a piece of the input file as a table or figure here. the list of parameters and available options for each must be given. Maybe an additional appendix should be a smaple input file, with comments}

\tcr{I am sending you the pretty latex example in an email}

\newpage
%------------------------------------------------------------------------------
%
%------------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{RESULTS} 
\label{sect::results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tcr{I think the time-adaptation results for TWIGL was be a great addition}

\tcr{re-do the figures 4 and 10 as discussed}

@@

The example is very simple and computes quickly, it entails a one dimensional, heterogeneous 400 cm slab with a varying absorption cross section.   Figure \ref{fig:slab} how the regions of the slab are divided and Table \ref{tab:1Dmat} shows the initial material properties.  Table \ref{tab:1Dslope} shows the ramp of the absorption cross-section of each region.

\begin{figure}[!htbp]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |}
\hline \hline \hline
  &   &   &   &   &   &    &    &   &   &   &   &   &   &   &   &   &   &   &   \\
  &   &   &   &   &   &    &    &   &   &   &   &   &   &   &   &   &   &   &   \\
1 & 1 & 1 & 1 & 2 & 3 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 4 & 4 & 1 & 1 & 1 & 1 \\
  &   &   &   &   &   &    &    &   &   &   &   &   &   &   &   &   &   &   &   \\
  &   &   &   &   &   &    &    &   &   &   &   &   &   &   &   &   &   &   &   \\
\hline \hline \hline
\end{tabular}
\caption{1-D heterogeneous slab region identification}
\label{fig:slab}
\end{center}
\end{figure}

\begin{table}[!htbp]
\begin{center}
\caption{1-D heterogeneous slab material properties and problem parameters}
\label{tab:1Dmat}
\begin{tabular}{lllllll}
\hline
Region & $D (cm)$ & $\Sigma_a (cm^{-1})$ & $\nu \Sigma_f (cm^{-1})$ & $v (cm/s)$ & $\beta$ & $\lambda (s^{-1})$ \\
\hline
1 & 1.0 & 1.1 & 1.1 & 1,000 & 0.006 & 0.1 \\
2 & 1.0 & 1.1 & 1.1 & 1,000 & 0.006 & 0.1 \\
3 & 1.0 & 1.1 & 1.1 & 1,000 & 0.006 & 0.1 \\
4 & 1.0 & 1.1 & 1.1 & 1,000 & 0.006 & 0.1 \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[!htbp]
\begin{center}
\caption{1-D heterogeneous slab absorption cross-section slope perturbation}
\label{tab:1Dslope}
\begin{tabular}{lllllll}
\hline
Material Property & 0.0 s & 0.1 s & 0.6 s & 1.0 s & 1.7 s \\
\hline
$\Sigma_{a,2} (cm^{-1})$ & 1.1 & 1.1 & 1.095 & 1.095 & 1.095 \\
$\Sigma_{a,3} (cm^{-1})$ & 1.1 & 1.1 & 1.09 & 1.09 & 1.1 \\
$\Sigma_{a,4} (cm^{-1})$ & 1.1 & 1.1 & 1.105 & 1.105 & 1.105 \\
\hline
\end{tabular}
\end{center}
\end{table}

Figure \ref{fig:power} shows the power at each macro time step as compared to the traditional brute force (full flux time discretization) method.  The strong correlation between the two curves shows that IQS is consistent with a proven method for a highly transient example.  Figure \ref{fig:conv} shows that IQS is not only consistent for this example, but also has a better error constant in the convergence study.  Figures \ref{fig:initial} - \ref{fig:final} plots shape changes in the IQS method, showing where the shape solution is necessary and a simple PRKE evaluation is inadequate.  Figure \ref{fig:conv} shows the error convergence for brute force and IQS methods.  This plot shows that IQS has consistent convergence slope for first and second order time schemes and that IQS has a better error constant for the convergence.  Table \ref{tab:1Ddt2} shows the results for time adaptation.  These results show that traditional IQS does not perform well with step doubling time adaptation and IQS P-C performs moderately better than brute force.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.8\linewidth]{\FiguresDir/1D_het_power_plot.png}
\caption{Power level of 1D heterogeneous example with $\Delta t = 0.01$}
\label{fig:power}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=5in,height=2in]{\FiguresDir/initial_flux.jpg}
\caption{Initial Flux Plot}
\label{fig:initial}
\end{center}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=5in,height=2in]{\FiguresDir/max_flux.jpg}
\caption{Flux Plot when Absorption Cross Section is at Minimum}
\label{fig:max}
\end{center}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=5in,height=2in]{\FiguresDir/final_flux.jpg}
\caption{Final Flux Computation (not steady-state)}
\label{fig:final}
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{TWIGL Benchmark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This benchmark problem originates from the Argonne National Lab Benchmark Problem Book.  It is a 2D, 2-group reactor core model with no reflector region shown in Figure \ref{fig:TWIGL_reg}.  Table \ref{tab:TWIGL_mat} shows the material properties of each fuel region and the ramp perturbation of Material 1.

@@

Figures \ref{fig:TWIGL_power} and \ref{fig:TWIGL_plots} show the IQS  solution as compared with the Brute Force solution.  It is important to note the IQS shape plot is scaled differently than the Brute Force flux plot because the amplitude term is not included, but the gradients of colors is comparable.  These plots show that IQS is consistent in more complex, higher dimensional problems in RATTLESNAKE.  Finally, Figure \ref{fig:TWIGL_conv} plots the error convergence of IQS and the Brute Force methods.  The curves show the impressive convergence of IQS for the highly transient TWIGL example.  Table \ref{tab:TWIGLdt2} shows the results for time adaptation.  The results show that both IQS methods perform exceptionally well compared to brute force.  It also shows that traditional IQS performed better with large $e_{max}$, while IQS P-C was better with smaller $e_{max}$.

\begin{figure}[!htbp]
\centering
\includegraphics[height=3.0in]{\FiguresDir/TWIGL_power_plot.png}
\caption{Power level comparison of TWIGL Benchmark with $\Delta t = 0.025$}
\label{fig:TWIGL_power}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\begin{subfigure}[!htbp]{0.4\textwidth}
\includegraphics[width=\textwidth]{\FiguresDir/ndiff_ramp_flux.jpg}
\caption{Brute force flux}
\end{subfigure}
\quad
\begin{subfigure}[!htbp]{0.4\textwidth}
\includegraphics[width=\textwidth]{\FiguresDir/iqs_ramp_shape.jpg}
\caption{IQS Shape}
\end{subfigure}
\caption{TWIGL Benchmark flux/shape comparison at $t=0.2$}
\label{fig:TWIGL_plots}
\end{center}
\end{figure}

@@

@@

Figure \ref{fig:LRA_plots} show the IQS  solution as compared with the Brute Force solution.    These plots show that IQS is consistent with Doppler feedback problems in RATTLESNAKE.  Figure \ref{fig:lra_conv} plots the error convergence of IQS and the Brute Force methods. Table  \ref{tab:LRAdt2} shows the time adaptation performance of both methods.  These results show that IQS, again, performs much better than the brute force method by taking significantly less diffusion solves while retaining similar accuracy.

\begin{figure}[!htbp]
\begin{center}
\begin{subfigure}[!htbp]{0.49\textwidth}
\includegraphics[width=\textwidth]{\FiguresDir/lra_power_profile.png}
\caption{Power Profile}
\end{subfigure}
\begin{subfigure}[!htbp]{0.49\textwidth}
\includegraphics[width=\textwidth]{\FiguresDir/lra_temp_profile.png}
\caption{Temperature Profile}
\end{subfigure}
\caption{LRA Benchmark power and temperature comparison}
\label{fig:LRA_plots}
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Appendix: aaaa}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tcr{putting stuff here for now}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\usepackage{vmargin}
\usepackage{color}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amstext}
\usepackage{amsbsy}
%\usepackage{mathbbol}
\usepackage{graphicx} 
\usepackage{verbatim}
\usepackage{csvsimple} 
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{listings}
\usepackage[numbers,sort&compress]{natbib}[2010/09/13]

@@

% tikz stuff
\usetikzlibrary{shapes,arrows,positioning}
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}
\tikzstyle{greenblock}=[rectangle, rounded corners, draw, align=center, top color=white, bottom color=green!20, ultra thick, minimum width=60mm, minimum height=15mm,]
\tikzstyle{blueblock}=[rectangle, rounded corners, draw, align=center, top color=white, bottom color=blue!20, ultra thick, minimum width=60mm, minimum height=15mm]
\tikzstyle{reddiamond}=[diamond, draw, align=center, top color=white, bottom color=red!20, ultra thick, minimum width=60mm, aspect=2]
\newcommand{\tikzback}[5]{
 \begin{pgfonlayer}{background}
  \path (#1.west |- #2.north)+(-0.5,0.75) node (a1) {};
  \path (#3.east |- #4.south)+(+0.5,-0.25) node (a2) {};
  \path[fill=yellow!10,rounded corners, draw=black!100, dashed] (a1) rectangle (a2);
   \path (#3.east |- #2.north)+(0,1.25)--(#1.west |- #2.north) node[midway] (#5-n) {};
   \path (#3.east |- #2.south)+(0,-0.35)--(#1.west |- #2.south) node[midway] (#5-s) {};
   \path (#1.west |- #2.north)+(-0.75,0)--(#1.west |- #4.south) node[midway] (#5-w) {};
 \end{pgfonlayer}}

% input stuff
\lstset{%
%  language=C++,
  showstringspaces=false,
% basicstyle=\scriptsize\ttfamily,
  basicstyle=\small\ttfamily,
  commentstyle=\color{inl@green},
%  keywordstyle=\bfseries,
%  escapeinside=$$
%  framesep=0pt,
%  rulesep=0pt,
  frame=single
}
% Make nice big tildes inside lstlistings instead of
% tiny ones.
\lstset{
    literate={~} {$\sim$}{1}
}

@@

\title{Improved Quasi-Static Methods in Rattlesnake}
\subtitle{Development and Implementation of Improved Quasi-Static (IQS) methods for time-dependent neutron diffusion and neutron transport solvers in Rattlesnake}
\author{ \normalsize
  \textbf{Zachary M. Prince$^\dagger$, Jean C. Ragusa$^\dagger$, Yaqi Wang$^\star$} \\
 \normalsize $^\dagger$Department of Nuclear Engineering \\
 \normalsize Texas A\&M University, College Station, TX, USA\\
 \normalsize $^\star$Idaho National Laboratory\\
 \normalsize \href{mailto:zachmprince@tamu.edu}{zachmprince@tamu.edu}, \href{jean.ragusa@tamu.edu}{jean.ragusa@tamu.edu}, \href{yaqi.wang@inl.gov}{yaqi.wang@inl.gov} 
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Because of the recent interest in reactor transient modeling and the restart of the Transient Reactor (TREAT) Facility, there has been a need for more efficient, robust methods in computation frameworks.  This is the impetus of implementing the Improved Quasi-Static method (IQS) in the Rattlesnake framework.  IQS has implemented with CFEM diffusion by factorizing flux into time-dependent amplitude and spacial- and weakly time-dependent shape.  The shape evaluation is very similar to a flux diffusion solve and is computed at large (macro) time steps.  While the amplitude evaluation is a PRKE solve where the parameters are dependent on the shape and is computed at small (micro) time steps.  IQS has been tested with a custom one-dimensional example, the TWIGL ramp benchmark, and LRA benchmark.  The results from each example include error convergence plots and performance with time adaptation.  These examples prove it to be a viable and effective method for highly transient cases. More complex cases are intended to be applied to further test the method and its implementation.

@@

\begin{figure}[!htpb]
\centering
\begin{tikzpicture}[every node/.style = {font=\normalsize}]

\node[greenblock](p1) at (0,0) {Solve shape equations \\ over macro time step};
\node[greenblock](p2) at (0,-2.5) {Compute PRKE parameters \\ over macro time step};
\node[greenblock](p3) at (0,-5) {Solve PRKE using micro \\ steps};
\node[greenblock](p4) at (0,-7.5) {Update $p$ and $\frac{dp}{dt}$};
\node[blueblock] (p5) at (0,-11) {Solve other physics \\ components};
\node[reddiamond] (check) at (0,-15) {Check for \\ convergence};
\node [above =0.1mm of p1] {\large{IQS Solve:}};
\node [above =0.1mm of p5] {\large{Multi-physics:}};

\tikzback{p1}{p1}{p4}{p4}{bk1}
\tikzback{p5}{p5}{p5}{p5}{bk2}

\draw[->,ultra thick](p1.south) -- (p2.north);
\draw[->,ultra thick](p2.south) -- (p3.north);
\draw[->,ultra thick](p3.south) -- (p4.north);
\draw [->,ultra thick] (p4.south)+(0,-0.25) -- node [above] {} (bk2-n);
\draw[->,ultra thick](p5.south)+(0,-0.25) -- (check.north);
%\draw[->,ultra thick](check.west) -- (-5,-15) -- node[above,sloped] {\large{no}}(-5,0) -- node[above] {}(bk1-w);
\draw[->,ultra thick](check.west) -- node[above,sloped] {\large{no}} (-5,-15) |-  node[above] {}(bk1-w);
\draw[->,ultra thick](check.south) -- node[right] {\large{yes}} ++(0,-2);

@@

The IQS executioner derives from the Transient executioner in MOOSE.  The IQS executioner contains a loop over micro time steps that computes the PRKE and then passes $p$ and $\frac{dp}{dt}$ for the Transient executioner to evaluate the shape equation at each macro step.  The PRKE is computed with a user specified option of backward-Euler, Crank-Nicolson, or SDIRK33.   The IQS executioner also supplements Transient Picard iteration process by adding its own error criteria:
\be
Error_{IQS}=\left|\frac{\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^{g,n}\right)}{\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^{g,0}\right)}-1\right|
\label{eq:eiqs}
\ee

@@

The input deck for IQS is very similar to the current transient diffusion input file.  The IQS input has a different executioner type and parameters.  The executioner type is simply IQS and input parameters include number of micro time steps, IQS error tolerance, and initial power.  The Rattlesnake transient action system currently requires a multi-app and transfer to compute and pass the initial $\phi$ and $\keff$, which is present in the transient input deck.  However, IQS also requires an initial evaluation of the adjoint flux, for the weighting function.  So another input file and multi-app transfer was made for the adjoint calculation.  \\

Below is the syntax for the executioner block for an IQS input file.  The \texttt{predictor\_corrector} logical determines whether to do IQS P-C or regular IQS.  The \texttt{IQS\_error\_tol} is the tolerance for the IQS error represented by Equation \ref{eq:eiqs} and will at most \texttt{picard\_max\_its} iterations until convergence.  The \texttt{prke\_scheme} defines the time discretization used for the PRKE evaluation. Where \texttt{RK} is SDIRK33, \texttt{CN} is Crank-Nicholson, and \texttt{IE} is implicit-Euler.
\begin{lstlisting}
[Executioner]
  type = IQS
  predictor_corrector = true/false
  picard_max_its = 5
  ...
  n_micro = 10000
  IQS_error_tol = 1e-7
  prke_scheme = 'RK'
[]
\end{lstlisting}

Since IQS needs to use the adjoint solution for the PRKE parameter evaluation, auxiliary variables need to be created for each group in the input file.  Below is an example of their definition:
\begin{lstlisting}
[AuxVariables]
  [./adjoint_flux_g0]
    family = LAGRANGE
    order = FIRST
  [../]
  [./adjoint_flux_g1]
    family = LAGRANGE
    order = FIRST
  [../]
  ...
[]
\end{lstlisting}

Below is the syntax for the multi-app block to perform forward and adjoint steady-state evaluations:
\begin{lstlisting}
[MultiApps]
 [./initial_solve]
   type = FullSolveMultiApp
   execute_on = initial
   input_files = initial.i
 [../]
 [./adjoint_solve]
   type = FullSolveMultiApp
   execute_on = initial
   input_files = adjoint.i
 [../]
[]
\end{lstlisting}

Below is the syntax for the Transfer block to copy the initial and adjoint solutions from the multi-apps.
\begin{lstlisting}
[Transfers]
 [./copy_solution]
   type = TransportSystemVariableTransfer
   direction = from_multiapp
   multi_app = initial_solve
   execute_on = initial
   from_transport_system = diff
   to_transport_system = diff
 [../]
 [./copy_adjoint]
   type = MultiAppVariableTransfer
   execute_on = initial
   direction = from_multiapp
   multi_app = adjoint_solve
   from_variables = 'sflux_g0 sflux_g1 ...'
   to_variables = 'adjoint_flux_g0 adjoint_flux_g1 ...'
 [../]
 [./copy_eigenvalue]
   type = EigenvalueTransfer
   execute_on = initial
   direction = from_multiapp
   multi_app = initial_solve
 [../]
[]
\end{lstlisting}

\newpage
%------------------------------------------------------------------------------
%
%------------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{RESULTS} 
\label{sect::results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The example is very simple and computes quickly, it entails a one dimensional, heterogeneous 400 cm slab with a varying absorption cross section.   Figure \ref{fig:slab} how the regions of the slab are divided and Table \ref{tab:1Dmat} shows the initial material properties.  Regions 2, 3, and 4 have slope perturbations at different points in time, Table \ref{tab:1Dslope} shows the values of the absorption cross-section in each region at the times of interest.  The values of $\Sigma_a$ between these times of interest are linear interpolations between the given values.

\begin{figure}[!htbp]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |}
\hline \hline \hline
  &   &   &   &   &   &    &    &   &   &   &   &   &   &   &   &   &   &   &   \\
1 & 1 & 1 & 1 & 2 & 3 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 4 & 4 & 1 & 1 & 1 & 1 \\
  &   &   &   &   &   &    &    &   &   &   &   &   &   &   &   &   &   &   &   \\
\hline \hline \hline
\end{tabular}
\caption{1-D heterogeneous slab region identification}
\label{fig:slab}
\end{center}
\end{figure}

\begin{table}[!htbp]
\begin{center}
\caption{1-D heterogeneous slab material properties and problem parameters}
\label{tab:1Dmat}
\begin{tabular}{llllll}
\hline
$D (cm)$ & $\Sigma_a (cm^{-1})$ & $\nu \Sigma_f (cm^{-1})$ & $v (cm/s)$ & $\beta$ & $\lambda (s^{-1})$ \\
\hline
1.0 & 1.1 & 1.1 & 1,000 & 0.006 & 0.1 \\

\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[!htbp]
\begin{center}
\caption{1-D heterogeneous slab absorption cross-section at times of interest}
\label{tab:1Dslope}
\begin{tabular}{llllllll}
\hline
Region & Material Property & 0.0 s & 0.1 s & 0.6 s & 1.0 s & 1.7 s \\
\hline
2 & $\Sigma_{a} (cm^{-1})$ & 1.1 & 1.1 & 1.095 & 1.095 & 1.095 \\
3 & $\Sigma_{a} (cm^{-1})$ & 1.1 & 1.1 & 1.09 & 1.09 & 1.1 \\
4 & $\Sigma_{a} (cm^{-1})$ & 1.1 & 1.1 & 1.105 & 1.105 & 1.105 \\
\hline
\end{tabular}
\end{center}
\end{table}

Figure \ref{fig:power} shows the power at each macro time step as compared to the traditional brute force (full flux time discretization) method.  The strong correlation between the two curves shows that IQS is consistent with a proven method for a highly transient example.  Figure \ref{fig:conv} shows that IQS is not only consistent for this example, but also has a better error constant in the convergence study.  Figure \ref{fig:conv} shows the error convergence for brute force and IQS methods.  This plot shows that IQS has consistent convergence slope for first and second order time schemes and that IQS has a better error constant for the convergence.  Table \ref{tab:1Ddt2} shows the results for time adaptation.  These results show that traditional IQS does not perform well with step doubling time adaptation and IQS P-C performs moderately better than brute force.

%Figures \ref{fig:initial} - \ref{fig:final} plots shape changes in the IQS method, showing where the shape solution is necessary and a simple PRKE evaluation is inadequate.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.49\textwidth]{\FiguresDir/1D_het_power_plot.png}
\includegraphics[width=0.5\textwidth]{\FiguresDir/1D_het_power_plot2.png}
\caption{Power level of 1D heterogeneous example}
\label{fig:power}
\end{figure}

%\begin{figure}[!htbp]
%\begin{center}
%\includegraphics[width=5in,height=2in]{\FiguresDir/initial_flux.jpg}
%\caption{Initial Flux Plot}
%\label{fig:initial}
%\end{center}
%\end{figure}
%
%\begin{figure}[!htbp]
%\begin{center}
%\includegraphics[width=5in,height=2in]{\FiguresDir/max_flux.jpg}
%\caption{Flux Plot when Absorption Cross Section is at Minimum}
%\label{fig:max}
%\end{center}
%\end{figure}
%
%\begin{figure}[!htbp]
%\begin{center}
%\includegraphics[width=5in,height=2in]{\FiguresDir/final_flux.jpg}
%\caption{Final Flux Computation (not steady-state)}
%\label{fig:final}
%\end{center}
%\end{figure}

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{TWIGL Benchmark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This benchmark problem originates from the Argonne National Lab Benchmark Problem Book \cite{ANL_BPB}.  It is a 2D, 2-group reactor core model with no reflector region shown in Figure \ref{fig:TWIGL_reg}.  Table \ref{tab:TWIGL_mat} shows the material properties of each fuel region and the ramp perturbation of Material 1.

@@

Figures \ref{fig:TWIGL_power} show the IQS  solution as compared with the Brute Force solution.  These plots show that IQS is consistent in more complex, higher dimensional problems in Rattlesnake.  Finally, Figure \ref{fig:TWIGL_conv} plots the error convergence of IQS and the Brute Force methods.  The curves show the impressive convergence of IQS for the highly transient TWIGL example.  Table \ref{tab:TWIGLdt2} and Figure \ref{fig:TWIGL_power_dt2} show the results for time adaptation.  The results show that both IQS methods perform exceptionally well compared to brute force.  It also shows that traditional IQS performed better with large $e_{max}$, while IQS P-C was better with smaller $e_{max}$.

%It is important to note the IQS shape plot is scaled differently than the Brute Force flux plot because the amplitude term is not included, but the gradients of colors is comparable.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.49\linewidth]{\FiguresDir/TWIGL_power_plot.png}
\includegraphics[width=0.5\linewidth]{\FiguresDir/TWIGL_power_plot2.png}
\caption{Power level comparison of TWIGL Benchmark}
\label{fig:TWIGL_power}
\end{figure}

%\begin{figure}[!htbp]
%\begin{center}
%\begin{subfigure}[!htbp]{0.4\textwidth}
%\includegraphics[width=\textwidth]{\FiguresDir/ndiff_ramp_flux.jpg}
%\caption{Brute force flux}
%\end{subfigure}
%\quad
%\begin{subfigure}[!htbp]{0.4\textwidth}
%\includegraphics[width=\textwidth]{\FiguresDir/iqs_ramp_shape.jpg}
%\caption{IQS Shape}
%\end{subfigure}
%\caption{TWIGL Benchmark flux/shape comparison at $t=0.2$}
%\label{fig:TWIGL_plots}
%\end{center}
%\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.8\linewidth]{\FiguresDir/TWIGL_power_plot_dt2.png}
\caption{Power level comparison of TWIGL Benchmark with time adaptation}
\label{fig:TWIGL_power_dt2}
\end{figure}

@@

Figure \ref{fig:LRA_plots} show the IQS  solution as compared with the Brute Force solution.    These plots show that IQS is consistent with Doppler feedback problems in Rattlesnake.  Figure \ref{fig:lra_conv} plots the error convergence of IQS and the Brute Force methods. Table  \ref{tab:LRAdt2} shows the time adaptation performance of both methods.  These results show that IQS, again, performs much better than the brute force method by taking significantly less diffusion solves while retaining similar accuracy.

\begin{figure}[!htbp]
\begin{center}
\begin{subfigure}[!htbp]{0.49\textwidth}
\includegraphics[width=\textwidth]{\FiguresDir/lra_power_profile.png}
\caption{Power Profile}
\end{subfigure}
\begin{subfigure}[!htbp]{0.49\textwidth}
\includegraphics[width=\textwidth]{\FiguresDir/lra_power_profile2.png}
\caption{Power Profile at Peak}
\end{subfigure}
\begin{subfigure}[!htbp]{0.49\textwidth}
\includegraphics[width=\textwidth]{\FiguresDir/lra_temp_profile.png}
\caption{Temperature Profile}
\end{subfigure}
\caption{LRA Benchmark power and temperature comparison}
\label{fig:LRA_plots}
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Appendix: aaaa}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\tcr{putting stuff here for now}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%It can be shown that the most appropriate weighting function $(w^g)$ is the initial adjoint flux $(\phi^{*g})$.  For brevity, the following definition will be applied: $\int_D\phi^{*g}(\vec{r})f(\vec{r})d^3r=\left(\phi^{*g},f\right)$
%\begin{align}
%& \quad \frac{dp}{dt}\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^g\right)+ p\frac{d}{dt}\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^g\right)= \nonumber \\
%& p\sum_{g=1}^G\left(\phi^{*g},\frac{\chi_p^g}{\keff}(1-\beta) \sum_{g'=1}^G  \nu^{g'} \Sigma_f^{g'} \varphi^{g'} + \sum_{g'\neq g}^G\Sigma_s^{g'\to g} \varphi^{g'} - \left( -\div D^g \grad  + \Sigma_r^g \right) \varphi^g\right)  \\
%& + \sum_{i=1}^I\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^g\lambda_i C_i) \nonumber
%\end{align}
%\be
%\frac{d}{dt}\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^gC_i)=\frac{1}{\keff}\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^g\beta_i\sum_{g'=1}^G\nu^{g'} \Sigma_f^{g' }\varphi^{g'})p - \sum_{g=1}^G(\phi^{*g},\chi_{d,i}^g\lambda_iC_i) \quad 1 \le i \le I 
%\ee
%
%In order to impose uniqueness of the factorization, one imposes:
%\be
